disaggregation: An \proglang{R} package for Bayesian spatial disaggregation modelling

### 2019-12-02 article.Rnw
Make iid effect clearer

For each of the model parameters and hyperparameters we specify priors. The regression parameters and intercept are given Gaussian priors, where the default priors are $\beta_0 \sim N(0, 2)$ and $\beta_i \sim N(0, 0.4)$. A penalised complexity prior is placed on the scale and range parameters of the random field \cite{fuglstad2018constructing} such that
\begin{align}
    P(\rho < \rho_{min}) &= \rho_{prob} \\
    P(\sigma > \sigma_{max}) &= \sigma_{prob}
\end{align}
where the values $\rho_{min}, \,\rho_{prob}, \,\sigma_{max}, \,\sigma_{prob}$ are set by the user. This prior shrinks the field towards a base model with zero variance and infinite range, in other words regularising towards a flatter field with smaller magnitude. The polygon-specific effects $u_1,...,u_N$ have Gaussian priors centered at 0 with standard deviation $u_{sd}$. A penalised complexity prior \cite{simpson2017penalising} such that $P(u_{sd} > sd_{max}) = sd_{prob}$ which shrinks towards a base model of no polygon-specific effect. The $sd_{max}$ and $sd_{prob}$ are set by the user.

@@

%
\begin{table}
\centering
\begin{tabular}{l|ll|ll}
 & \multicolumn{2}{|c|}{MCMC (94 hours)} & \multicolumn{2}{|c}{TMB (56 seconds)} \\
Parameter & Mean & SD & Mean & SD \\
\hline
Intercept & -3.09 & 0.33 & -3.12 & 0.27 \\
Slope 1 & 0.20 & 0.28 & 0.24 & 0.27 \\
Slope 2 & 0.32 & 0.21 & 0.30 & 0.21\\
Slope 3 & -0.36 & 0.20 & -0.37 & 0.20 \\
Slope 4 & -0.24 & 0.23 & -0.24 & 0.21 \\
iid $log(\tau)$ & 1.08 & 0.27 & 1.10 & 0.27 \\
$log(\sigma)$ & -3.34 & 0.59 & -3.55 & 0.59 \\
$log(\rho)$ & 0.72 & 0.31 & 0.56 & 0.30 \\
\end{tabular}
\caption{Fitted model parameter values using both MCMC and using \pkg{TMB} within the \pkg{disaggregation} package.}
\label{tab:mcmcresults}
\end{table}
%

>>>>

For each of the model parameters and hyperparameters we specify priors. The regression parameters and intercept are given Gaussian priors, where the default priors are $\beta_0 \sim N(0, 2)$ and $\beta_i \sim N(0, 0.4)$. A penalised complexity prior is placed on the scale and range parameters of the random field \cite{fuglstad2018constructing} such that
\begin{align}
    P(\rho < \rho_{min}) &= \rho_{prob} \\
    P(\sigma > \sigma_{max}) &= \sigma_{prob}
\end{align}
where the values $\rho_{min}, \,\rho_{prob}, \,\sigma_{max}, \,\sigma_{prob}$ are set by the user. This prior shrinks the field towards a base model with zero variance and infinite range, in other words regularising towards a flatter field with smaller magnitude. The polygon-specific effects $u_1,...,u_N$ have Gaussian priors centered at 0 with standard deviation $\sigma_{u}$ (where the precision $\tau_{u} = 1/\sigma_{u}^2$). A penalised complexity prior \cite{simpson2017penalising} such that 
\begin{equation}
P(\sigma_{u} > \sigma_{u, max}) = \sigma_{u, prob}
\end{equation}
which shrinks towards a base model of no polygon-specific effect. The $\sigma_{u, max}$ and $\sigma_{u, prob}$ are set by the user.

@@

%
\begin{table}
\centering
\begin{tabular}{l|ll|ll}
 & \multicolumn{2}{|c|}{MCMC (94 hours)} & \multicolumn{2}{|c}{TMB (56 seconds)} \\
Parameter & Mean & SD & Mean & SD \\
\hline
Intercept & -3.09 & 0.33 & -3.12 & 0.27 \\
Slope 1 & 0.20 & 0.28 & 0.24 & 0.27 \\
Slope 2 & 0.32 & 0.21 & 0.30 & 0.21\\
Slope 3 & -0.36 & 0.20 & -0.37 & 0.20 \\
Slope 4 & -0.24 & 0.23 & -0.24 & 0.21 \\
$log(\tau_u)$ & 1.08 & 0.27 & 1.10 & 0.27 \\
$log(\sigma)$ & -3.34 & 0.59 & -3.55 & 0.59 \\
$log(\rho)$ & 0.72 & 0.31 & 0.56 & 0.30 \\
\end{tabular}
\caption{Fitted model parameter values using both MCMC and using \pkg{TMB} within the \pkg{disaggregation} package.}
\label{tab:mcmcresults}
\end{table}
%
